Behavior Driven Development in Haskell

### 2012-05-29 paper.tex
Sum up Doctests implementation

TBD: kazu: how to obtain evidence from Haddock markup.
Old version uses Haddock API but now uses GHC API directly. Why?

TBD: kazu: escape from HUnit. Why?

TBD: kazu: Old version executes one GHCi for each function examples.
But new version executes one GHCI per module.
Drastic speed up. Do We need a graph for execution time?

>>>>

\begin{itemize}
    \item
        Doctest uses the GHC API to extract Haddock comments.
    \item
        It uses the GHC API directly, so that it can more easily
        support old GHC versions.  Each release of Haddock only
        supports the latest GHC version.
    \item
        Doctest use GHCi to verify examples.
    \item
        It reuses the same GHCi session for all examples.
    \item
        Examples from the same Haddock comment are grouped together,
        and share the same scope.
    \item
        The scope is cleared with \verb|:reload| before a new
        Example group is started.
    \item
\end{itemize}
